Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-07-31 volunteer-clouds-ieee-ci-si.tex
Footnote converted to reference
@fergunet you shouldn't use footnotes to point to documents, create a bib entry and cite it instead.

Recent works propose the use of cloud computing services for the components of 
client-server distributed EAs. Cloud resources 
can reduce operational costs by outsourcing both hardware and software maintenance 
to the cloud provider. Another advantage is that they enable the provisioning of computing resources beyond what 
is available in most laboratories, allowing researches to 
scale algorithms at reasonable costs. Researchers have proposed the use of 
public clouds such as Amazon EC2 \cite{CloudScale}, Google App Engine\cite{di2013towards} 
and DropBox~\cite{mericloud}. The use of JavaScript to implement server side components, %FERGU: he puesto mejor el de revista en lugar del del CEC
gives software developers certain advantages in the cloud paradigm. JavaScript is a first-class citizen
in most Platforms as a Service (PaaS) as many support the Node.js framework 
\footnote{\url{https://strongloop.com/strongblog/a-comparison-of-node-js-paas-hosting-providers/}}. Also many web services %FERGU: he validado esta frase con un footnote, pero si quieres lo paso a referencias
have native JavaScript libraries and use JSON for data interchange. Another advantage is that 
developers can use the same software tools for both client and server side development. 
Besides the advantages to deal with the same language in the full stack as previously mentioned, 
this also facilitates the interoperability of the exchanged data types.
%Ayuda con la mini conclusion FERGU: mira la última frase de arriba

>>>>

Recent works propose the use of cloud computing services for the components of 
client-server distributed EAs. Cloud resources 
can reduce operational costs by outsourcing both hardware and software maintenance 
to the cloud provider. Another advantage is that they enable the provisioning of computing resources beyond what 
is available in most laboratories, allowing researches to 
scale algorithms at reasonable costs. Researchers have proposed the use of 
public clouds such as Amazon EC2 \cite{CloudScale}, Google App Engine\cite{di2013towards} 
and DropBox~\cite{mericloud}. The use of JavaScript to implement server side components, %FERGU: he puesto mejor el de revista en lugar del del CEC
gives software developers certain advantages in the cloud paradigm. JavaScript is a first-class citizen
in most Platforms as a Service (PaaS) as many support the Node.js framework \cite{wood13:nodejs:paas}. Also many web services %FERGU: he validado esta frase con un footnote, pero si quieres lo paso a referencias
have native JavaScript libraries and use JSON for data interchange. Another advantage is that 
developers can use the same software tools for both client and server side development. 
Besides the advantages to deal with the same language in the full stack as previously mentioned, 
this also facilitates the interoperability of the exchanged data types.
%Ayuda con la mini conclusion FERGU: mira la última frase de arriba
